An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
fix minor typo

CloudCoder supports two types of exercises:  {\em function-based}
exercises and {\em whole-program} exercises.  Function-based exercises are
very similar to CodingBat exercises: the student is required to write
a function (or method, depending on the programming language) that takes some number of parameter values,
does a computation, and returns a result value.
Students are given a description of
what the function should do, and a couple of example inputs with
expected results.  Writing a new function-based exercise
requires a description, some skeleton code (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding expected results.
Test cases can be marked as ``secret'' so that students don't see their
inputs or expected results, to discourage students from writing a special case to
recognize each input.

@@

Denny et. al. have studied novice syntax errors\cite{Denny:2012:SEE:2325296.2325318}
using data collected from the CodeWrite system.
CodeWrite is similar to CloudCoder, except that students create
exercises and test cases for each other to solve, and are evaluated on
the quality of their practice exercises.

Lane et. al. describe Intention-Based Scoring (IBS)\cite{Lane:2005:ISA:1047344.1047471},
an approach to building an ITS for programming whereby human
judges to score or code {\em charettes}, or assignments students work on in a
timed, closed-lab environment.  IBS derives from prior work on
identifying ``bugs'' in online protocols, and as such attempts to
identify places where students have a ``bug'' in their development
process.  This approach, while labor-intensive, shows some promise in
developing an ITS for programming assignments.

Zingaro et. al. built the Python Classroom Response
System\cite{Zingaro:2013:FCP:2445196.2445369}, a system similar to
CloudCoder, except that it focuses on supporting in-class programming
questions for a class that uses a {\em Peer Instruction} pedagogical approach.

Pritchard et. al. present CS Circles\cite{Pritchard:2013:CCI:2445196.2445370},
an interactive on-line
Python curriculum that embeds short questions, some of which involve
programming, directly into the text.  This sort of interactive text
shows great promise for developing open, interactive courses.

>>>>

CloudCoder supports two types of exercises:  {\em function-based}
exercises and {\em whole-program} exercises.  Function-based exercises are
very similar to CodingBat exercises: the student is required to write
a function (or method, depending on the programming language) that takes some number of parameter values,
does a computation, and returns a result value.
Students are given a description of
what the function should do, and a couple of example inputs with
expected results.  Writing a new function-based exercise
requires a description, some skeleton code (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding expected results.
Test cases can be marked as ``secret'' so that students don't see the
inputs or expected results, to discourage students from writing a special case to
recognize each input.

@@

Denny et.\ al. have studied novice syntax errors\cite{Denny:2012:SEE:2325296.2325318}
using data collected from the CodeWrite system.
CodeWrite is similar to CloudCoder, except that students create
exercises and test cases for each other to solve, and are evaluated on
the quality of their practice exercises.

Lane et.\ al. describe Intention-Based Scoring (IBS)\cite{Lane:2005:ISA:1047344.1047471},
an approach to building an ITS for programming whereby human
judges to score or code {\em charettes}, or assignments students work on in a
timed, closed-lab environment.  IBS derives from prior work on
identifying ``bugs'' in online protocols, and as such attempts to
identify places where students have a ``bug'' in their development
process.  This approach, while labor-intensive, shows some promise in
developing an ITS for programming assignments.

Zingaro et.\ al. built the Python Classroom Response
System\cite{Zingaro:2013:FCP:2445196.2445369}, a system similar to
CloudCoder, except that it focuses on supporting in-class programming
questions for a class that uses a {\em Peer Instruction} pedagogical approach.

Pritchard et.\ al. present CS Circles\cite{Pritchard:2013:CCI:2445196.2445370},
an interactive on-line
Python curriculum that embeds short questions, some of which involve
programming, directly into the text.  This sort of interactive text
shows great promise for developing open, interactive courses.
